SVG: The Paper

### 2022-07-21 Analysis/index.Rmd
some tidying up of sup mat

### Faster people are more predictable

Is this worth doing?

@@

```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each indivdiaul observer."}
a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60) %>%
  mutate(time_taken_s = as.numeric(scale(log(time_taken)))) -> timedat

@@

```{r fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each individual observer."}
timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition) -> plt

@@

```{r}

@@

# Trial level

```{r}

@@

ggplot(a_trl, aes(trial, meanb, group = observer)) + geom_jitter(alpha = 0.25) + 
  geom_path(alpha = 0.1) + facet_wrap(~condition) +
  geom_smooth(method = "lm", group = 1)

@@

We can model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.

```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$. We can see that a two component mixture model will capture most of the variance in intial target selection."}

@@

```{r}
gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
  group_by(c, .variable) %>%
  summarise(value = mean(.value), .groups = "drop") %>%
  pivot_wider(names_from = ".variable", values_from = "value") -> am

>>>>

@@

It seems like shorter trials are easier for the model to predict, in both the feature and conjunction case (though the relationship appears to be clearer in the feature condition).

```{r, message = FALSE, warning = FALSE, fig.cap="The relationship between the time taken to complete a trial and how predictable it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each indivdiaul observer."}

a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60) %>%
  mutate(time_taken_s = as.numeric(scale(log(time_taken)))) -> timedat

@@

```{r, message = FALSE, warning = FALSE, fig.cap="The relationship between the time taken to complete a trial and how predictible it is. Dots show empirical data, and the shaded ribbon shows the fixed-effects of a multi-level model. The lines give posterior samples from each individual observer."}

timedat %>% data_grid(condition, time_taken_s = seq_range(time_taken_s, 5)) %>%
  add_epred_draws(m, re_formula = NA, ndraws = 100) %>%
  ggplot(aes(time_taken_s, fill = condition)) + 
  stat_lineribbon(aes(y = .epred), alpha = 0.5, .width = c(0.53, 0.97)) +
  geom_jitter(data = timedat, aes(y = acc, colour = condition), 
              alpha = 0.05, width = 0, height = 0.005, colour = "black") +
  scale_x_continuous("scaled log response time (log seconds)") + 
  scale_y_continuous("model accuracy")  + 
  scale_colour_discrete(guide = "none") +
  coord_cartesian(ylim = c(0.4, 0.9)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  facet_wrap(~ condition) -> plt

@@

```
This relationship appears to hold true if you look at how long it takes participants to select individual targets as well.

```{r, message = FALSE, warning = FALSE, fig.cap = "The relationship between the time taken to complete a single target selection and how predictible it is."}

@@

```{r eval=FALSE, fig.cap="The relationship between mean weight of the next target and trial number", message=FALSE, include=FALSE}

@@

ggplot(a_trl, aes(trial, meanb, group = observer)) + geom_jitter(alpha = 0.25) + 
  geom_path(alpha = 0.1) + facet_wrap(~condition) +
  geom_smooth(method = "lm", group = 1) +
  ylab('Mean weight of next target') +
  xlab('Trial number')

@@

Can we model this as multi-level beta distribution? Yes, although it seems like people are in one of two clusters.

```{r fig.cap = "The mean posterior plot for the truncated normal distriubtions for (*left*) $x$ and (*right*) $y$. We can see that a two component mixture model will capture most of the variance in intial target selection.", warning = FALSE}

@@

Both models give a similar distribution of target weights and accuracies, and in both cases, participants who start in a corner are easier to predict.

```{r, fig.cap = "(Top): a count of initial weight values predicted from both methods (mixture and multi-level). (Bottom left): the proportion of times the first selection was correct for both methods. (Bottom right): as lambda (the model parameter underlying initial weight) increases, accuracy increases ie. the model is moore accurate for the cases where participants are selecting a corner as their initial target selection."}
gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
  group_by(c, .variable) %>%
  summarise(value = mean(.value), .groups = "drop") %>%
  pivot_wider(names_from = ".variable", values_from = "value") -> am
